Examining Whether Approximate Visualizations Impact Perception of Corrected Visualizations

### 2016-11-14 paper/paper.tex
Statistical analysis section

>>>>

Analysis of each study question will have four independent variables: visualization number (interval), type of data displayed (categorical), level of approximation (interval), and presentation technique (categorical).
We anticipate visualization number and type of data displayed will have no effect on our results, as they do not pertain to our research questions.
Should they have no effect, we will then discard these terms from our analysis and not report on them further.
Further, each participant will be treated as a random effect.

We are asking three types of questions in our study with different dependent variables:
\begin{enumerate}
\item Was there a difference between the precise and approximate visualizations (categorial dependent variable)
\item Which airline or state had the most or least flights (categorical dependent variable)
\item How many flights were on a particular airline or from a particular state (interval depdendent variable)
\item Confidence in answers to the above questions (interval dependent variable)
\end{enumerate}

\begin{table}[!t]
% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Example statistical analysis table for categorical dependent variables}
\label{table_example}
\centering
\begin{tabular}{|c||c|c|c|c|}
\hline
Study parameter & Est. & SE & Z & p\\
\hline
\hline
Presentation Technique & & & & \\
\hline
Approximate Sample Amount & & & & \\
\hline
Technique * Sample Amount & & & & \\
\hline
\end{tabular}
\end{table}

\begin{figure}[!t]
  \centering
  \includegraphics[width=2.5in]{blankheatmap.png}
  \caption{Example heatmap to demonstrate interaction}
  \label{fig:blank_heatmap}
\end{figure}

We will analyze our data through regressions.
For questions with categorical responses, we will use a factorial logistic regression (\texttt{glm} with a \texttt{binomial} family in R).
We will use a factorial ANOVA (\texttt{anova} on \texttt{lm} in R) for questions with interval responses.
Table \ref{table_example} shows what we expect our regression tables to show.

We will likely have to conduct post-hoc Tukey tests to differentiate between study conditions.
We will present the results of those tests graphically.
For example, Figure \ref{fig:blank_heatmap} shows how we will present the amount of bias present in different study conditions for numerical questions, such as question 3 above.
